High-Dimensional Regularized Discriminant Analysis

### 2017-10-19 reports/paper-hdrda-anonymous.Rnw
anonymous version of paper because journal does double blind

\author{
\name{John A. Ramey\textsuperscript{a}\thanks{CONTACT John A. Ramey. Email: johnramey@gmail.com}, Caleb K. Stein\textsuperscript{b}, Phil D. Young\textsuperscript{c}, and Dean M. Young\textsuperscript{d}}
\affil{\textsuperscript{a}Novi Labs, Austin, TX, USA; \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA; \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA; \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA}
}

@@

@@

\section{Acknowledgements}

This research did not receive any specific grant from funding agencies in the
public, commercial, or not-for-profit sectors. We thank Mrs. Joy Young for her
numerous recommendations that enhanced the quality of our writing.

>>>>

@@

\textbf{Word Count:} 7,059

@@

### 2017-10-19 reports/title-page.tex
anonymous version of paper because journal does double blind

\author{
\name{John A. Ramey\textsuperscript{a}\thanks{CONTACT John A. Ramey. Email: johnramey@gmail.com}, Caleb K. Stein\textsuperscript{b}, Phil D. Young\textsuperscript{c}, and Dean M. Young\textsuperscript{d}}
\affil{\textsuperscript{a}Novi Labs, Austin, TX, USA;\\ \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA;\\ \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA;\\ \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA}
}

@@

>>>>

\author{
\name{John A. Ramey\textsuperscript{a}\thanks{CONTACT John A. Ramey. Email: johnramey@gmail.com}, Caleb K. Stein\textsuperscript{b}, Phil D. Young\textsuperscript{c}, and Dean M. Young\textsuperscript{d}}
\affil{\textsuperscript{a}Novi Labs, Austin, TX, USA, \url{johnramey@gmail.com};\\ \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA, \url{stein.caleb@gmail.com};\\ \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA, \url{Philip_Young@baylor.edu};\\ \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA, \url{Dean_Young@baylor.edu}}
}

@@

\section*{Acknowledgements}

This research did not receive any specific grant from funding agencies in the
public, commercial, or not-for-profit sectors. We thank Mrs. Joy Young for her
numerous recommendations that enhanced the quality of our writing.
